Process-based phenotypes: an application to the Cellular Phenotype Ontology

### 2011-11-22 trunk/paper/drinking.tex

A second kind of regulatory abnormalities are related to the {\em
  onset} of a process. With respect to a reference process, a
particular kind of process may be {\em delayed} ({\tt PATO:0000502})
or {\em premature} ({\tt PATO:0000694}). For example,

Further kinds include deviations from distribution patterns. For
example, a kind of process that is normally {\em rhythmic} can be
abnormal in that it is {\em arrhythmic}...

>>>>

There are further types of deviation from a distribution pattern. For
example, a kind of process that is normally {\em rhythmic} can be
abnormal in that it is {\em arrhythmic}. A typical example of this
kind of process is {\em Heart beating} ({\tt GO:0060047}), in which
{\em Cardiac muscle contraction} ({\tt GO:0060048}) processes occur in
a rhythmic pattern. In {\em Cardiac dysrhythmia}, however, {\em
  Cardiac muscle contraction} processes occur arrhythmically, and we
consider this to be an abnormality of the regulation of {\em Cardiac
  muscle contraction}.

A second kind of regulatory abnormalities are related to the {\em
  onset} of a process. With respect to a reference process, a
particular kind of process may be {\em delayed} ({\tt PATO:0000502})
or {\em premature} ({\tt PATO:0000694}). For example, {\em Delayed
  apoptosis} refers to an abnormality of {\em Regulation of apoptosis}
in which apoptosis is induced later than normal.
